\chapter*{Acknowledgements}
\emph{Had I the heavens' embroidered cloths,\\
	Enwrought with golden and silver light,\\
	The blue and the dim and the dark cloths\\
	Of night and light and the half-light,\\
	I would spread the cloths under your feet:\\
	But I being poor have only my dreams;\\
	I have spread my dreams under your feet;\\
	Tread softly because you tread on my dreams.\\
	\bf{W. B. Yeates}\\
}

This thesis presents more than three years of work at the University of Cambridge, during which time I have had the privilege to meet and work with many fantastic people. Please allow me to begin by thanking those of you who have supported and encouraged me in my research work -- without you, nothing that I achieved would have been possible.

First and foremost, I would like to thank my supervisors, David Klenerman and Sophie Jackson. Thank you both for your continued support and encouragement, despite the somewhat unusual structure and focus of my PhD. Thank you for giving me the freedom to pursue my research interests and for allowing me to find a path that is my own, if somewhat unconventional.

To my colleagues in the Klenerman and Jackson groups, thank you all for making my time in the Chemistry Department so enjoyable. Particular thanks are due to:

\begin{itemize}
\item[] Mathew, for many many invaluable conversations about data, sizing and thresholding. Your enthusiasm for research, your attention to detail and your ability to get things done are all phenomenal. I wish you great success and great happiness in your future research career. Enjoy your life as an expatriate.
\item[] Vladas, you were a fantastic collaborator and Masters student throughout your research project, even though it was somewhat ``wetter'' than you might have hoped. The Holliday Junctions that you prepared have been invaluable to our research on oligomer sizing and have given the group many useful insights. Thank you also for sharing Marmalade!
\item[] Alex, for your amazing skills with hardware description languages and all of your custom FPGA correlators. Without your expertise, none of this research could have been done. Thank you also for your patience in the face of my lack of physics knowledge and your assisstance with signal generators.
\item[] Kristina, for your help with TIRF experiments, as well as for many interesting discussions about data analysis and statistics. As a scientist, you are an inspiration.
\item[] Magnus, for all your support with pyFRET, in particular your enthusiasm to test new functionality and all your suggestions for improvements. Your encouragement took this from just an idea to something real and made me a much better sofware engineer in the process.
\item[] Yu, thank you for many interesting discussions about data, your honesty, and your eventual agreement that actually I am quite clumsy in the lab!
\item[] Steve, thank you for many helpful discussions. Your enthusiasm and insight have dramatically improved my understanding of optics, light and physics generally. Your guidance and collaboration helped to bring many ideas from theoretical concept to concrete reality.
\end{itemize}

Gratitude is also owing to the Algorithms Group at Illumina, who made my internship there such an interesting and memorable experience. In particular, I would like to thank Ole and Jared for all their patience and understanding, as well as for your support in bringing such an interesting project to reality.

To George, my partner. Thank you for your unconditional support, your infinite love and the best conversation in the world. Thank you for introducing me to the magic that is programming and for your many hours debugging my early spaghetti attempts at writing code. You have brought more to my life than you can imagine.

To James, my colleague and friend, thanks are owing for many years of great discussions, tea and cynicism. Thanks for your support and for telling me to get my act together.

Finally to my family: Granny, Mum and Peter, thank you all so much for your help and support throughout my life. Thank you for teaching me about the truly important things: kindess, integrity and honesty. And Grandad, thank you for your early enouragement on my scientific journey. Thank you for teaching me about evidence and proof. I hope you would be proud of me today. 