\chapter{Introduction}
\label{chap:intro}
\section{Introduction}
This chapter provides a general introduction to the contextual background of the work presented in this thesis. First, we provide a general overview of the physical phenomena of fluorescence and F\"{o}rster resonance energy transfer (FRET). We describe the application of these phenomena to the study of biological molecules and the common experimental and analytical techniques used in these research areas. We then present an overview of techniques of statistical analysis, with a particular focus on model-based Bayesain inference. We present common sampling-based techniques for Bayesian statistical analysis and describe why Bayesian inference is a useful tool in the analysis of single-molecule fluorescence data.

\section{Fluorescence and FRET}
\subsection{The Physical Basis of Fluorescence}
Fluorescence is the physical phenomenon by which a molecule that has absorbed a photon of electromagnetic radiation and which is in an excited state relaxes via non-radiative processes, such as vibrational interactions, rotation and translation in its medium and then  emits a photon, hence returning to its ground state. Owing to the intramolecular transitions occurring prior to emission, the photon emitted is of a lower energy than the photon absorbed. The difference in energy between the absorbed and emitted photons is termed the Stokes shift~\cite{Albani2011} and is a characteristic of the energy levels available to the excited molecule.  

The typical timescale for a single fluorescence excitation-emission cycle is approximately $10^{-10} - 10^{-7}$ s. This timescale is dominated by the lifetime of the excited state, (typically $10^{-10} - 10^{-7}$ s), whilst excitation and emission processes have a much shorter timescale (absorption $10^{-15}$ s, relaxation $10^{-12} - 10^{-10}$ s)   

\subsection{The Physical Basis of FRET}

\section{Single Molecule Fluorescence Microscopy}
\subsection{Confocal Microscopy}
\subsection{Instrumentation}
\subsection{Data Acquisition}
\subsection{Data Analysis}

\section{Forster Resonance Energy Transfer}
F\"{o}rster resonance energy transfer (FRET) is a non-radiative energy transfer process that can occur between chromophoric molecules~\cite{forster48}. The degree of energy transfer is dependent on the fluorophore distance, allowing FRET to be used as a ``molecular ruler"~\cite{stryer67}, to determine intramolecular distances. Since FRET was first used to measure the distance between two fluorescent dyes on individual molecules bound to a surface~\cite{ha96}, single-molecule FRET (smFRET) has become a popular tool to investigate the structure and dynamics of biomolecules, both on a surface and diffusing freely in solution~\cite{haran03, schuler02, weiss00}.

\section{Single Molecule Fluorescence Microscopy}
\subsection{Overview}
\subsection{Confocal Microscopy}
In a confocal smFRET experiment, biological molecules are labelled with two fluorescent dyes. The emission spectrum of the donor dye ($D$) is chosen to overlap with the excitation spectrum of the acceptor ($A$). When the donor and acceptor are sufficiently close in space, exciting the donor dye results in FRET and fluorescent emission from the acceptor dye. The FRET efficiency, $E$, which describes the proportion of excitation energy transferred from the donor to the acceptor, depends on the distance, $r$ between the two dyes (Eq.~\ref{eq:efficiency}) and $R_0$, the F\"{o}rster distance, a dye dependent constant that describes the dye separation at which 50\% energy transfer is achieved (Fig.~\ref{fig:fig1_instrumentation} C)

\begin{equation}
E = \frac{1}{1 + (\frac{r}{R_0})^6} 
\label{eq:efficiency}
\end{equation}

Consequently, the distance between the two fluorophores can be determined from the ratio of donor and acceptor photons emitted during an excitation event (Eq.~\ref{eq:Eprod}).

Experimentally, a collimated laser beam, is used to illuminate an extremely dilute solution of labelled molecules. When a labelled molecule diffuses through the laser beam, the donor dye is excited and photons are emitted from both donor and acceptor dyes.  Emitted photons are collected through the objective and separated into donor and acceptor streams for collection and analysis (Fig.~\ref{fig:fig1_instrumentation} A, B). 

For a single fluorescent burst, the FRET efficiency, $E$, can be calculated as (Eq~\ref{eq:Eprod}):

\begin{equation}
E = \frac{n_A}{n_A + \gamma \cdot n_D}
\label{eq:Eprod}
\end{equation} 

for $n_A$ and $n_D$ detected acceptor and donor photons respectively and $\gamma$ an experimentally determined instrument-dependent correction factor. During the course of a smFRET experiment, several thousand fluorescent bursts are collected and used to construct FRET efficiency histograms. These histograms can be used to identify populations of fluorescent species~\cite{ha96}, typically by fitting multiple gaussian distributions.

\subsection{Total Internal Fluorescence Miroscopy}

\subsection{Epifluorescent Microscopy}

\subsection{Super-Resolution Microscopy}

\section{Probabilistic Inference and Bayesian Statistics}
\subsection{Bayesian Statistics}
\subsection{Sampling Techniques}
